\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-30 Report/project_report.tex
Commited to committing
I'm all about dat plot, bout dat plot, no label

Next, we define a vector of three parameters:
\begin{align}
\hat{\Vec{y}} &= \bbm \alpha & \beta & \gamma \ebm^T = \frac{1}{\hat{Z}^{(j)}_{C_1}} \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & 1 \ebm ^T
\end{align}
The feature position in camera frame $C_i$ can be expressed as
\begin{align}
\hat{\Vec{p}}_{C_i}^{f_j C_i} = \hat{\Vec{C}}_{i1} \hat{\Vec{p}}_{C_1}^{f_j C_1}  + \hat{\Vec{p}}_{C_i}^{C_1 C_i}
\end{align}
With our state parameters, we can use this equation to define three functions:
\begin{align}
    \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \\ h_3 (\hat{\Vec{y}}) \ebm 
    & = \hat{\Vec{C}}_{i1} \bbm \alpha \\ \beta \\ 1 \ebm + \gamma  \hat{\Vec{p}}_{C_i}^{C_1 C_i} \notag \\
    & = \bbm C_{11} \alpha + C_{12} \beta + C_{13} + \gamma \hat{x}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{21} \alpha + C_{22} \beta + C_{23} + \gamma \hat{y}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{31} \alpha + C_{32} \beta + C_{33} + \gamma \hat{z}_{C_i}^{C_1 C_i} 
        \ebm 
\end{align}
The camera measurement error can then be written as
\begin{align}
\Vec e(\hat{\Vec{y}}) = \hat{\Vec{z}}_i^{(j)} - \frac{1}{h_3 (\hat{\Vec{y}}) } \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \ebm
\end{align}
The least squares linear system then becomes
\begin{align}
(\Vec  E^T \Vec W ^{-1} \Vec E ) \delta \Vec{y}^*  = - \Vec{E}^T\Vec{W}^{-1}\Vec{e}(\hat{\Vec{y}})
\end{align}
where
\begin{align}
\Vec E &= \frac{\partial \Vec e}{\partial \hat{\Vec{y}}}
& &
\text{and}
&
\Vec W &= \text{diag}\left\{ \Vec{R}_1^{(j)}, \hdots, \Vec{R}_N^{(j)} \right\}
\end{align}
with $\Vec{R}_i^{(j)} = \text{diag}\left\{\sigma^2_{u'}, \sigma^2_{v'}\right\}$.

@@

However, the EKF assumes that measurement errors are linear in the error in the state and have an additive zero-mean Gaussian noise component that is \textit{uncorrelated} to the error in the state.
Since the error in the feature positions \textit{is} correlated to the error in the state, $\Vec{r}^{(j)}$ cannot be used in the EKF directly.
Figure \ref{fig:nullspace} shows the effect of attempting to use this error directly in the EKF.
The correlation between the measurement error and the state causes the filter to behave very poorly after a small number of time steps.

@@

    \caption{Effect of nullspace projection on MSCKF performance. The correlation between the measurement error and the state causes the filter to behave very poorly after a small number of time steps.}
    \label{fig:nullspace}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{figs/trajectory_groundtruth}
    \caption{Vicon ground truth for sensor head motion (blue) and feature positions (red) in the ``Starry Night'' dataset.}
    \label{fig:trajectory_groundtruth}
\end{figure}

@@

@@

    \caption{Comparison of cumulative Root Mean Squared Error (RMSE) of MSCKF, SWF, and IMU integration for three different synthetic maps generated based on the IMU data in the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' and ``SWF'' refer to the number of features in the dataset (20, 40 or 60).}
    \label{fig:comp_3}
\end{figure}

>>>>

Next, we define a vector of three parameters:
\begin{align}
\hat{\Vec{y}} &= \bbm \alpha & \beta & \gamma \ebm^T = \frac{1}{\hat{Z}^{(j)}_{C_1}} \bbm \hat{X}^{(j)}_{C_1} & \hat{Y}^{(j)}_{C_1} & 1 \ebm ^T
\end{align}
We can express the feature position in camera frame $C_i$ in terms of its position in camera frame $C_1$:
\begin{align}
\hat{\Vec{p}}_{C_i}^{f_j C_i} = \hat{\Vec{C}}_{i1} \hat{\Vec{p}}_{C_1}^{f_j C_1}  + \hat{\Vec{p}}_{C_i}^{C_1 C_i}
\end{align}
With our state parameters, we can use this equation to define three functions:
\begin{align}
    \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \\ h_3 (\hat{\Vec{y}}) \ebm 
    & = \hat{\Vec{C}}_{i1} \bbm \alpha \\ \beta \\ 1 \ebm + \gamma  \hat{\Vec{p}}_{C_i}^{C_1 C_i} \notag \\
    & = \bbm C_{11} \alpha + C_{12} \beta + C_{13} + \gamma \hat{x}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{21} \alpha + C_{22} \beta + C_{23} + \gamma \hat{y}_{C_i}^{C_1 C_i} \\[0.5em]
            C_{31} \alpha + C_{32} \beta + C_{33} + \gamma \hat{z}_{C_i}^{C_1 C_i} 
        \ebm 
\end{align}
The camera measurement error can then be written as
\begin{align}
\Vec e(\hat{\Vec{y}}) = \hat{\Vec{z}}_i^{(j)} - \frac{1}{h_3 (\hat{\Vec{y}}) } \bbm h_1 (\hat{\Vec{y}}) \\ h_2 (\hat{\Vec{y}}) \ebm
\end{align}
The least squares linear system then becomes
\begin{align}
(\Vec  E^T \Vec W ^{-1} \Vec E ) \delta \Vec{y}^*  = - \Vec{E}^T\Vec{W}^{-1}\Vec{e}(\hat{\Vec{y}})
\end{align}
where
\begin{align}
\Vec E &= \frac{\partial \Vec e}{\partial \hat{\Vec{y}}}
& &
\text{and}
&
\Vec W &= \text{diag}\left\{ \Vec{R}_1^{(j)}, \hdots, \Vec{R}_N^{(j)} \right\}
\end{align}
with $\Vec{R}_i^{(j)} = \text{diag}\left\{\sigma^2_{u'}, \sigma^2_{v'}\right\}$.

@@

However, the EKF assumes that measurement errors are linear in the error in the state and have an additive zero-mean Gaussian noise component that is \textit{uncorrelated} to the state.
Since the term $\Vec{H}_{f}^{(j)} \widetilde{\Vec{p}}_G^{f_j G}$ \textit{is} correlated to the state, $\Vec{r}^{(j)}$ is not of the correct form for the EKF and must be modified to de-correlate it from the state.
Figure \ref{fig:nullspace} shows the effect of attempting to use $\Vec{r}^{(j)}$ directly in the EKF.
The correlation between the measurement noise and the state causes the filter estimates to drift further from the true values than with a modified, de-correlated measurement error.

@@

    \caption{Effect of correlation between measurement noise and filter state on MSCKF performance. The correlation between the measurement error and the state causes the filter estimates to drift further from the true values than with a modified, de-corellated measurement error.}
    \label{fig:nullspace}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{figs/trajectory_groundtruth}
    \caption{Vicon ground truth for sensor head motion and feature positions in the ``Starry Night'' dataset.}
    \label{fig:trajectory_groundtruth}
\end{figure}

@@

\subsection{Experiment 3: Effect of feature density}
Finally, we investigated the effect of feature density on the performance of both the MSCKF and SWF.
For this experiment, we modified the ``Starry Night'' dataset by creating synthetic feature distributions with larger spatial extents and more features than the original dataset.
We retained the original IMU data, but simulated camera measurements with lower measurement noise.
Figure \ref{fig:trajectory_groundtruth_100lessnoisy} shows the feature distribution for the 100-feature synthetic dataset.

\begin{figure}
    \centering
    \includegraphics[width=0.48\textwidth]{figs/trajectory_groundtruth_100lessnoisy}
    \caption{Modified ``Starry Night'' dataset with 100 synthetic features. The sensor trajectory is identical to the original dataset.}
    \label{fig:trajectory_groundtruth_100lessnoisy}
\end{figure}

@@

    \caption{Comparison of cumulative Root Mean Squared Error (RMSE) of MSCKF, SWF, and IMU integration for three different synthetic maps generated based on the IMU data in the dataset interval $k\in[1215,1715]$. The numbers next to ``MSCKF'' and ``SWF'' refer to the number of features in the dataset (40, 60 or 100).}
    \label{fig:comp_3}
\end{figure}
